### 2008-03-27 trunk/Papers/rabbit-from-hat/howto.tex
wrote some text in sect 4-5

\section{Generating succinct expressions}
\label{sec:howto}

>>>>

\section{Succinct expressions in planning}
\label{sec:howto}

The primary reason for FF's failure to compute a plan is due to the
fact that it computes all instances of all actions and literals before
it starts the search.  This heuristic allows it to avoid performing
unifications during the search, and is thus a good idea on the
planning competition benchmarks, whose domain sizes are not very
large.  However, in our case FF has to deal with potentially huge
numbers of instances.  If we assume a maximum plan size of 10, the
action \textbf{S-takefrom-1} alone has $31 \cdot 15^3 \cdot 4 =
418,500$ instances -- and there are ten copies of it!  For grammars of
more realistic sizes, it is easy to imagine how the number of
instances might run into the trillions.

\begin{itemize}
\item PKS: don't have to instantiate
\item new PKS: can build names on the fly by function application
\item external modules seem a comparatively small part, but if nothing
  else, they save an argument slot.
\end{itemize}
